\papertitle

### 2012-10-12 manuscript.tex
Intro update.

Due to restrictive payload weights, much previous work on guidance of flapping wing 
with cameras depends on powerful offboard processing. Baek demonstrated altitude control 
with an external camera\cite{baek:altitude}. de Croon et al. demonstrated obstacle 
avoidance with an onboard camera\cite{delfly:avoid}. [However, these papers have not studied
the system blah blah blah.]

>>>>

In contrast, there is little previous work on guidance of flapping wing MAVs. Baek demonstrated 
altitude control with an external camera\cite{baek:altitude}. de Croon et al. demonstrated obstacle 
avoidance with an onboard camera and offboard processing\cite{delfly:avoid}. [However, these papers 
do not study the system blah blah blah.]
